\batcave: Bayesian Analysis Tools for Context-Aware Variant Evaluation

### 2019-08-19 NAR_DRAFT.tex
minor changes
add figure 3 to results description

\usepackage{NAR-natbib}
\bibliographystyle{unsrtnat}
\usepackage{color}
\usepackage{xfrac}
\newcommand{\rngcomment}[1]{{\color{red}RNG: #1}}
\newcommand{\bkmcomment}[1]{{\color{blue}BKM: #1}}
\newcommand{\batcave}{BATCAVE }
\newcommand{\beginsupplement}{%
        \setcounter{table}{0}
        \renewcommand{\thetable}{S\arabic{table}}%
        \setcounter{figure}{0}
        \renewcommand{\thefigure}{S\arabic{figure}}%
     }
% Enter dates of publication
\copyrightyear{2008}
\pubdate{31 July 2009}
\pubyear{2009}
\jvolume{37}
\jissue{12}

@@

@@

The algorithm has low computational overhead, and in principle there should be no bar to simply incorporating it into existing variant calling algorithms.
\bkmcomment{coming}

@@

\bibliography{caller_paper}
\clearpage
\onecolumn
\beginsupplement
\section{Supplememtary Figures}

>>>>

\usepackage{NAR-natbib}
\bibliographystyle{unsrtnat}
\usepackage{color}
\usepackage{xfrac}
\newcommand{\rngcomment}[1]{{\color{red}RNG: #1}}
\newcommand{\bkmcomment}[1]{{\color{blue}BKM: #1}}
\newcommand{\batcave}{BATCAVE }
\newcommand{\beginsupplement}{%
        \clearpage
        \onecolumn
        \setcounter{table}{0}
        \renewcommand{\thetable}{S\arabic{table}}%
        \setcounter{figure}{0}
        \renewcommand{\thefigure}{S\arabic{figure}}%
     }
% Enter dates of publication
\copyrightyear{2008}
\pubdate{31 July 2009}
\pubyear{2009}
\jvolume{37}
\jissue{12}

@@

Figure \ref{NAR-ppv_fig} takes a consolidated view of classification accuracy and calibration in the portion of the posterior probability distribution relevant to clinicians and researchers.
For any probability between .6 and .95 \batcave is better calibrated than Mutect.
Essentially, for any posterior probability above .7 MuTect has a false positive rate around 8\%, which \batcave has a false positive rate that increases as posterior probability decreases.
The cost of this compression is recall.
At any posterior probability \batcave returns a larger fraction of all positive calls than MuTect.

@@

The algorithm has low computational overhead, and in principle there should be no bar to simply incorporating it into existing variant calling algorithms.

@@

\bibliography{caller_paper}

\beginsupplement
\section{Supplememtary Figures}
